### Team Porifera

**Q1**

Match the following types of real-world data to their equivalent R type and explain your reasoning.

-   Real world data: scientific names, the count of plants in a quadrat, whether or not it rained on a sequence of days, and the reaction times of birds to disturbances in seconds

    -   scientific names - character

    -   count of plants in a quadrat - integer

    -   whether or not it rained on a sequence of days - logical

    -   the reaction times of birds to disturbances in seconds - numeric

-   R types: logical, integer, numeric, and character

**Q2**

Use this code chunk to answer the following questions.

```{r}
bird_mass_g <- c(100.1, 99.2, 99.3, NA, 100.0, 101.5, 94.7, 99.2, 108.2)
bird_mass_narm <- na.omit(bird_mass_g)
mean_mass <- mean(bird_mass_narm)
sd_mass <- sd(bird_mass_narm)
is_outlier <- bird_mass_narm > mean_mass + 1 * sd_mass
num_outliers <- sum(is_outlier)
num_outliers
```

-   In plain english, what does this code chunk do?

    -   This code determines how many bird weights are considered outliers when the standard deviation is set to 1.

-   Two of the lines have mistakes that keep the code from doing what it's supposed to. What are the mistakes and how would you fix them?

    -   I omitted NA from the initial vectors by using na.omit in the second line. Then I made sure that was the object in place for each operation that follows.

-   What are the types of `bird_mass_g`, `is_outlier`, and `num_outliers`?

    -   bird_mass_g - numeric

    -   is_outlier - logical

    -   num_outliers - integer

**Q3**

How could you change the first line of code in the following chunk so that `median_count` comes out to `5L`? I reordered the vectors.

```{r}
quad_counts <- c(5L, 5L, 2L, 19L, 0L, 4L, 12L, 7L)
valid_quads <- c(1, 2, 3, 5, 7)
quad_counts2 <- quad_counts[valid_quads]
median_count <- median(quad_counts2)
median_count
```
